\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-07-01 paper.tex
Update on Overleaf.

While parts of the architecture ({\sc Spark}, {\sc Oro}) have been deployed with
external execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2008shary} is the main one,
written in the \emph{Procedural Reasoning System (PRS)} language~\cite{Ingrand1996}.
We have also developed the Python-based {\sc pyRobots}~\cite{lemaignan2015pyrobots} that
provides a large set of high-level actions and an event-based architecture well
suited for prototyping. They both rely on extensive integration with the knowledge
base, that serves as the primary source of semantics for the decision making process.

@@

Execution control systems for social robots are expected 
to account not only for the task achievement but also for the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint}. {\sc Shary} supports
such mechanisms. It allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables each agent to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms.

@@

\subsubsection{Action Refinement, Execution and Monitoring}\label{sec:action}

@@

These five questions should not be considered independently from each others and
often require, on the contrary, to be dealt with in a single decision step. The
human-aware task and motion planners which we have built, are instances of
systems which have been designed to deal with such intricate decision issues.

\fixme{Rachid: the reviewer 2 asks for a better connection between these general
questions and the specific approaches that we take}

@@

The components that we have presented so far build a \emph{knowledge-oriented}
architecture: knowledge is explicitly stored in one central and consistent
repository of facts, accessible for all modules. It relies on a strict formalism
(OWL statements), with a well defined vocabulary (stated in the common-sense
ontology). These first two points lead to a loosely-coupled architecture
where modules can be removed or replaced easily by other ones as long as they
share the same semantics: modules are defined by the knowledge they produce or
consume.

@@

We have presented in this paper a large deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the model of integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We combine it further with a situated natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal
interactive communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimise plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2007,Sisbot2008,Mainprice2011,Pandey2011,sisbot2012human,kruse2013human}, and finally present two
execution controller, the PRS-based {\sc
Shary}~\cite{clodic2008shary,fiore2014,clodic2014key}
and the event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.

>>>>

While parts of the architecture ({\sc Spark}, {\sc Oro}) have been deployed with
external execution controllers (like {\sc Cram}~\cite{Beetz2010} or the BERT
platform~\cite{Lallee2010b}, as reported in~\cite{Lemaignan2010}), we have also
developed dedicated robot controllers which integrate the whole stack introduced
in Figure~\ref{fig|archi}. {\sc Shary}~\cite{clodic2009} is the main one,
written in the \emph{Procedural Reasoning System (PRS)} language~\cite{Ingrand1996}.
We have also developed the Python-based {\sc pyRobots}~\cite{lemaignan2015pyrobots} that
provides a large set of high-level actions and an event-based architecture well
suited for prototyping. They both rely on extensive integration with the knowledge
base, that serves as the primary source of semantics for the decision making process.

@@

Execution control systems for social robots are expected 
to account not only for the task achievement but also for the communication
and monitoring acts needed to support human-robot interactive task
achievement~\cite{Rich1997,Sidner2005,sebanz2006joint}. {\sc Shary} supports
such mechanisms~\cite{Clodic2007smc}. It allows
to bind action execution to \emph{communication policies} in order to produce
multi-modal signals towards the human and to react to human actions and signals. The
\emph{communication act} is the central concept in this formalism. It
represents an information exchange between the two agents and plays the role of
a transition condition. This exchange can be realised through speech, through an
expressive motion or a combination of the two. It enables the robot as well as the human to
communicate their beliefs about the task to be achieved, in order to share
mutual knowledge and to synchronise their activities.  This is done through
real-time task-based situation assessment achieved by the combination of {\sc
Shary} monitoring processes and {\sc Oro} inference
mechanisms. In Shary, each action description contains not only the way to execute it and monitor it, but also the way to initiate it (e.g. in the case of a shared action, the way both agents need to commit to the task), to suspend (or cancel or stop) it (and for each case the way this transition has to be shared with the human partner if any). This is supported by a description of the beliefs of each involved agent concerning the action achievement process and a set of monitoring processes allowing to update it

@@

\subsubsection{Human-Aware Action Refinement, Execution and Monitoring}\label{sec:action}

@@

These five questions should not be considered independently from each other and
often require, on the contrary, to be dealt with in a single decision step. The
human-aware task and motion planners which we have built, are instances of
systems which have been designed to deal with such intricate decision issues.

They are in fact taken into account in most, if not in all, the
components and at different levels of abstraction: at the shared plan
level as well as at action refinement and execution level.

Repeatedly, the choice of the next action, of who has to act (the human, the robot
or both of them) and when to perform it is made by {\sc Shary} with
the help of {\sc HATP}, based on perspective-taking and
situation assessment ({\sc Spark} and {\sc Oro} as well as on
estimation of the human mental state ({\sc Shary} with the help of
{\sc Oro}).

Where and how to perform an action is made by a full set of on-line
planning functions provided by {\sc Mhp} that computes not only
trajectories but also the pertinent placements and postures based not
only on geometric information but also estimation of the human current
mental state and preferences ({\sc Oro}).

@@

The components that we have presented so far build a \emph{knowledge-oriented}
architecture: knowledge is explicitly stored in one central and consistent
repository of facts, accessible to all modules. It relies on a strict formalism
(OWL statements), with a well defined vocabulary (stated in the common-sense
ontology). These first two points lead to a loosely-coupled architecture
where modules can be removed or replaced easily by other ones as long as they
share the same semantics: modules are defined by the knowledge they produce or
consume.

@@

We have presented in this paper a large deliberative architecture designed for
social robots. While most of its sub-components have been independently
presented in other publications, we offer here for the first time a perspective
on the model of integration of these components into a coherent and consistent
system for social human-robot interaction. We have first exposed our underlying
knowledge model based on Description Logics~\cite{Lemaignan2010} and some of the
resulting reasoning capabilities pertaining to disambiguation~\cite{Ros2010b}
and mental modelling~\cite{warnier2012when} that are shown to effectively
scaffold interaction using human-level semantics and cognitive skills. We have
then presented our approach to symbol grounding, build on an amodal situation
assessment environment~\cite{Sisbot2011} that supports perspective
taking~\cite{Marin2008,Ros2010}. We combine it further with a situated natural
language processor~\cite{Lemaignan2011a} to provide complete multi-modal
interactive communication.  The paper also covers our symbolic social task
planner~\cite{Alili2008, Alili2009, Lallement2014}: it generates predictive
plans of the human actions that enable the system to plan for joint human-robot
tasks. It can also make use of social heuristics to optimise plans for social
acceptability. We briefly mention our human-aware motion and manipulation
planner~\cite{Sisbot2007,Sisbot2008,Mainprice2011,Pandey2011,sisbot2012human,kruse2013human}, and finally present two
execution controller, the PRS-based {\sc
Shary}~\cite{clodic2009,fiore2014,clodic2014key}
and the event-driven {\sc pyRobots}~\cite{lemaignan2015pyrobots}.
